---
title: "Documentation"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(sf)
library(beeswarm)
library(knitr)
library(stargazer)
library(readxl)
library(mapview)
library(viridis)
library(DT)
library(scales)
library(vtable)
library(lfe)

mapviewPWS <- function(pwsid,...){
  url <- paste0("https://geoconnex.us/ref/pws/",pwsid)
  pws <- sf::read_sf(url)
  mapview::mapview(pws,...)
}
```

# Data Preperation

## Find utilities by ownership type

This is the inventory of all utilities that fill out the EAR
```{r inventory}
inv <- read_excel("Data/EAR/inventory.xlsx",
                  sheet = "SDWISWaterSystemInventory071620") %>% filter(WaterSystemType=="C")

bounds <- sf::read_sf("https://opendata.arcgis.com/datasets/fbba842bf134497c9d611ad506ec48cc_0.geojson")
```

We have to correct the rates data PWSIDs
```{r corrections}
rates <- readr::read_csv("Data/OWRS/summary_table_cleanedv2.csv")
corr <- read_csv("Data/OWRS/correction.csv")
rates <- left_join(rates,corr,by=c("utility_name"))
rates$pwsid.y <- NULL
rates <- rename(rates,pwsid=pwsid.x)
rates$pwsid[which(!is.na(rates$`corrected rates PWSID`))] <- rates$`corrected rates PWSID`[which(!is.na(rates$`corrected rates PWSID`))]
```

Now have to correct rate tier prices

```{r correct rates pwsis}
# merge in original bill units
original_units <- read_csv("Data/OWRS/summary_table.csv") %>% select(utility_name,bill_unit) 
rates <- left_join(rates,original_units,by="utility_name") 
#recalculate tier prices that were converted from ccf to kg with appropriate conversion factor dividing by 0.748052kgal/ccf to convert back to $/ccf, and then again to convert  to $/kgal. Original calculation was in a wrong unit of $/(ccf/0.748)
rates$Tier_price[which(rates$bill_unit.y=="ccf")]<-rates$Tier_price[which(rates$bill_unit.y=="ccf")]/(0.748052^2)
```
## Create Billing data
Now calculate prep to calculate water bills
```{r calculate bills}
# set values for non-discretionary water use
gpcd <- 50
days_month <- 365/12
hh_cons_person <- gpcd*days_month

#expand grid of all combinations of utility and household size (1-7)
names <- c(unique(rates$utility_name))
hhsize <- c(1:7)
hhsize <- expand.grid(hhsize,names)
names(hhsize) <- c("hhsize","utility_name")
hhsize$utility_name <- as.character(hhsize$utility_name)

#join to main table
rates <- left_join(rates,hhsize,by="utility_name")
rates$consumption <- (rates$hhsize * hh_cons_person)/1000
```

write function to calculate water bills
```{r bill_calculate}

rates <- arrange(rates,pwsid,utility_name,hhsize,Tier_number)
rates$Tier_volume[which(!is.na(rates$Tier_price) & is.na(rates$Tier_volume))] <- 10^10

rates <- rates %>% 
  group_by(utility_name,hhsize) %>%
  mutate(next_tier_volume = lead(Tier_volume),
         prev_tier_volume = case_when(
           Tier_number == 1 ~ 0,
           Tier_number > 1 ~ lag(Tier_volume)
         ),
         Tier_width = case_when(
           Tier_number == 1 & !is.na(next_tier_volume) ~ Tier_volume,
           Tier_number >1 ~ Tier_volume - prev_tier_volume,
           is.na(next_tier_volume) ~ 10^10,
           ),
         vol_in_tier = case_when(
           bill_type == "Uniform" & Tier_number ==1 ~ consumption,
           consumption <= prev_tier_volume ~ 0,
           consumption > Tier_volume ~ Tier_width,
           consumption > prev_tier_volume & consumption <= Tier_volume ~ consumption - prev_tier_volume#,
          # consumption > Tier_volume ~ Tier_width,
           #consumption >= Tier_volume & is.na(next_tier_volume) ~ consumption - Tier_volume#,
           #consumption >= Tier_volume & is.na(next_tier_volume) ~ consumption - Tier_volume
         )
  ) 

rates$vol_revenue <- NA
rates$vol_revenue = rates$Tier_price * rates$vol_in_tier

rates$vol_revenue[which(rates$bill_type=="1.49*usage_ccf")] <- 1.49*rates$consumption[which(rates$bill_type=="1.49*usage_ccf")]*0.748052
rates$vol_revenue[which(rates$bill_type=="3.04*usage_ccf*1.333")] <- 3.04*rates$consumption[which(rates$bill_type=="3.04*usage_ccf*1.333")]*1.333*0.748052

bills <- rates %>% group_by(pwsid,
                            utility_name,
                            bill_type,
                            hhsize,
                            consumption,
                            service_charge) %>%
  summarise(volumetric_charge = sum(vol_revenue,na.rm=TRUE))

bills$bill <- bills$service_charge + bills$volumetric_charge

```
Now we need to categorize them all by ownership type. To Recover ownership type, we read in the latest EAR
```{r type}
ear13 <- read_tsv("Data/EAR/earsurveyresults_2013ry.zip",col_types="ccdcccdddc")
 ear14 <- read_tsv("Data/EAR/earsurveyresults_2014ry.zip",col_types="ccdcccdddc")
 ear15 <- read_tsv("Data/EAR/earsurveyresults_2015ry.zip",col_types="ccdcccdddc")
 ear16 <- read_tsv("Data/EAR/earsurveyresults_2016ry.zip",col_types="ccdcccdddc")
 ear17 <- read_tsv("Data/EAR/earsurveyresults_2017ry.zip",col_types="ccdcccdddc")
 ear18 <- read_tsv("Data/EAR/earsurveyresults_2018ry.zip",col_types="ccdcccdddc")
 ear19 <- read_tsv("Data/EAR/earsurveyresults_2019ry.zip",col_names=c("PWSID",
                                                                      "Survey",
                                                                      "Year",
                                                                      "SectionName",
                                                                      "QuestionName",
                                                                      "QuestionResults",
                                                                      "SurveyID",
                                                                      "SectionID",
                                                                      "QuestionID",
                                                                      "Pk"), col_types="ccdcccdddc")
ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18,ear19)
save(ear,file="Data/ear.rds")
#load("Data/ear.rds")
ownership <- ear %>% filter(QuestionName %in% c("Water System Ownership",
                                    "IsWholesaler")) %>% 
  select(PWSID, 
         Year, 
         QuestionName, 
         QuestionResults,
         QuestionID,
         Pk) %>% 
  pivot_wider(id_cols = c(PWSID, Year),
              names_from = QuestionName,
              values_from = QuestionResults,
              names_repair="unique") %>% unnest(cols=c("Water System Ownership","IsWholesaler") ) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(`Water System Ownership` %in% c(
    "Privately owned business (non-community)",
    "Privately owned Mutual Water Company or Association",
    "Privately owned, non-PUC-regulated (Community Water System)",
    "Local Government",
    "Privately owned, PUC-regulated, for profit water company"
    
  )) 

```
## Census data

Get all the variables
```{r census_cars}
census_api_key("b25f8b1b7bf10561c9cbc3a20a4d2572677f1f05")
options(tigris_use_cache = TRUE)
vars <- load_variables(2019, "acs5", cache = TRUE)
census_vars2 <- c(median_income="B19013_001",
                 pop_in_hh_with_income_assistance="B09010_002",
                 pop_in_hh_with_no_income_assistance="B09010_008",
                 hh_inc_5k="B19001_002",
                 hh_inc_12.5k="B19001_003",
                 hh_inc_17.5k="B19001_004",
                 hh_inc_22.5k="B19001_005",
                 hh_inc_27.5k="B19001_006",
                 hh_inc_32.5k="B19001_007",
                 hh_inc_37.5k="B19001_008",
                 hh_inc_42.5k="B19001_009",
                 hh_inc_47.5k="B19001_010",
                 hh_inc_55k="B19001_011",
                 hh_inc_67.5k="B19001_012",
                 hh_inc_87.5k="B19001_013",
                 hh_inc_112.5k="B19001_014",
                 hh_inc_137.5k="B19001_015",
                 hh_inc_175k="B19001_016",
                 hh_inc_gr200k="B19001_017",
                 hh_income_count = "B19001_001")

```

Lets get all the Municipal boundaries
```{r}
st <- get_acs(year=2019,geography = "state",
                  variables = "B01003_001", geometry = TRUE) %>% filter(NAME=="California")
pl <- get_acs(year=2019,geography = "place",
                  variables = "B01003_001", geometry = TRUE, state= "CA") 

vars <- load_variables(2019, "acs5", cache = TRUE)
```

Let's get all the Census Block Groups
```{r}
# bg <- get_acs(year=2019,geography = "block group",
#                   variables = census_vars2, geometry = TRUE, state= "CA") 
# save(bg, file="Data/census_blockgroups.rds")
load("Data/census_blockgroups.rds")
```

Let's get all the Urbanized Areas and combine them into super areas.
```{r}
ua <- get_acs(year=2019,geography = "urban area",
                  variables = c("B01003_001","B19013_001"), geometry = TRUE, output="wide")
ua<-rename(ua,Pop=B01003_001E)
ua <- ua[st,]
ua2 <- st_as_sf(rgeos::gUnaryUnion(as_Spatial(ua)))
ua2 <- select(ua,Pop)
ua3 <- st_union(ua)
ua4 <- aggregate(ua2,ua3,FUN=sum, join=st_intersects)
```

## Descriptive stats
Now we categorize all utilities in the SDWIS Inventory by type
```{r merge_type}
own <- ownership %>% group_by(PWSID,`Water System Ownership`) %>% add_tally() %>% ungroup() %>% group_by(PWSID) %>% add_tally() %>% ungroup()
own1 <- filter(own,n == nn)
own1 <- distinct(own,PWSID,.keep_all=TRUE)
own2 <- filter(own, n != nn)
own2 <- own2 %>% 
  distinct(PWSID, `Water System Ownership`, .keep_all=TRUE) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(Year==maxYear) %>% 
  group_by(PWSID) %>%
  add_tally()

own1 <- select(own1, PWSID, `Water System Ownership`,Year)
own2 <- select(own2, PWSID, `Water System Ownership`,Year)
own <- bind_rows(own1,own2)
own <- own %>% group_by(PWSID) %>% mutate(maxYear=max(Year)) %>% ungroup() %>% filter(Year == maxYear)

rm(own1,own2)


d <- left_join(inv,own, by="PWSID")
d <- select(d, PWSID, PWS_Name, County, Pop, ServConn, `Water System Ownership`)
d$log10PopCat <- floor(log10(d$Pop))

```

## some distributive plots
```{r, results='asis'}
d <- filter(d,`Water System Ownership` != "Privately owned business (non-community)")
x <- data.frame(table(d$log10PopCat,d$`Water System Ownership`))
x <- x%>%pivot_wider(id_cols = Var1,names_from = Var2, values_from=Freq)

datatable(x,extensions="Buttons",options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv')))



y <- d %>% 
  mutate(TotPop = sum(Pop,na.rm=TRUE),
         PropPop = Pop/TotPop) %>%
  group_by(log10PopCat,`Water System Ownership`) %>% 
  summarise(Population = sum(Pop,na.rm=TRUE),
            Pop_percent = 100*sum(PropPop,na.rm=TRUE)) %>%
  pivot_wider(id_cols = `log10PopCat`, 
              names_from = `Water System Ownership`,
              values_from = c(Population,Pop_percent))

datatable(y,extensions="Buttons",options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv')))

p<- ggplot(d, aes(x=log10(Pop), color=`Water System Ownership`), size=4) +
  geom_density(lwd=2) + 
  scale_color_viridis_d() + 
  theme_dark() + 
  theme(legend.position=c(0.69, 0.85)) +
  xlab("log(base 10) of Service Population")

p
```
Spatial demonstration figure. Show utility boundaries, municipal boundaries, and censusblock groups
```{r}
b <- bounds %>% select(PWSID) 
d.b <- d %>% inner_join(b,by="PWSID") %>% st_as_sf()
pal <- magma(n = length(unique(pl$NAME)), direction = -1)

bkfield <- st_transform(filter(ua,GEOID=="04681"),4326)
d1 <- d.b[bkfield,,op=st_intersects]
pl1 <- st_transform(pl,4326)[bkfield,,op=st_intersects]

m <- mapview(d1,zcol="Water System Ownership", alpha=0.8, layer.name = "Water System Boundaries") +
  mapview(pl1, stroke=TRUE, color="red", alpha.regions=0, layer.name = "Municipal Boundaries",lwd=2,legend=TRUE,col.regions="red")
mapshot(m,"Figures/Map1.html")

d.x <- st_buffer(st_transform(d.b,3310),dist=0)

```
```{r, include=FALSE}

bg.x <- bg %>% filter(variable=="median_income") %>%
  select(GEOID,NAME,estimate,geometry) %>% rename(median_income = estimate) %>%
  st_transform(3310) %>%
  st_buffer(dist=0) %>%
  mutate(AreaBlockGroup = st_area(.))


bg.bounds <- st_intersection(d.x,bg.x) 
```

Bakersfield example 
```{r example, results="asis}
bkfield <- filter(ua,GEOID=="04681")
bg.bounds <- st_transform(bg.bounds,4326)
bkfield <- st_transform(bkfield,4326)
bkfield <- bg.bounds[bkfield,]

bk.bound <- d.b[bkfield,,op=st_intersects]

m2<-mapview(bkfield,zcol="median_income",layer.name="Census Block Group - Median HH Income") + mapview(bk.bound, alpha=1, layer.name = "Water System Boundaries", stroke=TRUE,color="black",col.regions="black", alpha.regions=0, lwd=4,legend=TRUE)
#mapshot(m2,"Figures/Map2.html")
```


Calculate affordability
```{r calcualte affordability}
bg.bounds <- st_transform(bg.bounds,3310)
bg.bounds$Area_BlockGroupPWS <- st_area(bg.bounds)
bg.bounds$Percent_BlockGroupinPWS <- bg.bounds$Area_BlockGroupPWS/bg.bounds$AreaBlockGroup


pws.income <- bg.bounds %>% st_drop_geometry() %>%
  left_join(bg,by="GEOID") %>%
  filter(variable %in% c('hh_inc_5k',
                 'hh_inc_12.5k',
                 'hh_inc_17.5k',
                 'hh_inc_22.5k',
                 'hh_inc_27.5k',
                 'hh_inc_32.5k',
                 'hh_inc_37.5k',
                 'hh_inc_42.5k',
                 'hh_inc_47.5k',
                 'hh_inc_55k',
                 'hh_inc_67.5k',
                 'hh_inc_87.5k',
                 'hh_inc_112.5k',
                 'hh_inc_137.5k',
                 'hh_inc_175k',
                 'hh_inc_gr200k')) %>%
  group_by(PWSID,variable) %>%
  summarise(estimate=sum(estimate*Percent_BlockGroupinPWS)) %>% 
  ungroup() %>%
  mutate(var2=case_when(variable=="hh_inc_5k" ~ 1,
                 variable=="hh_inc_12.5k" ~ 2,
                 variable=="hh_inc_17.5k" ~ 3,
                 variable=="hh_inc_22.5k" ~ 4,
                 variable=="hh_inc_27.5k" ~ 5,
                 variable=="hh_inc_32.5k" ~ 6,
                 variable=="hh_inc_37.5k" ~ 7,
                 variable=="hh_inc_42.5k" ~ 8,
                 variable=="hh_inc_47.5k" ~ 9,
                 variable=="hh_inc_55k" ~ 10,
                 variable=="hh_inc_67.5k" ~ 11,
                 variable=="hh_inc_87.5k" ~ 12,
                 variable=="hh_inc_112.5k" ~ 13,
                 variable=="hh_inc_137.5k" ~ 14,
                 variable=="hh_inc_175k" ~ 15,
                 variable=="hh_inc_gr200k" ~ 16,)) %>% 
  arrange(PWSID,var2) %>% 
  group_by(PWSID) %>%
  mutate(cum_inc_sum = cumsum(estimate),
         percentile_inc = 100*cum_inc_sum/sum(estimate)) %>%
  ungroup() %>%
  mutate(perc_dist20=abs(as.numeric(percentile_inc)-20),
         perc_dist50=abs(as.numeric(percentile_inc)-50)) %>%
  group_by(PWSID) %>%
  filter(perc_dist20==min(perc_dist20) | 
         perc_dist50==min(perc_dist50)) %>%
  mutate(percentile=case_when(var2==min(var2)~"20th Percentile",
                              var2==max(var2)~"50th Percentile"),
         income_perc=case_when(var2==1 ~ 5000,
                               var2==2 ~ 12500,
                               var2==3 ~ 17500,
                               var2==4 ~ 22500,
                               var2==5 ~ 27500,
                               var2==6 ~ 32500,
                               var2==7 ~ 37500,
                               var2==8 ~ 42500,
                               var2==9 ~ 47500,
                               var2==10 ~ 55000,
                               var2==11 ~ 67500,
                               var2==12 ~ 87500,
                               var2==13 ~ 112500,
                               var2==14 ~ 137500,
                               var2==15 ~ 175000,
                               var2==16 ~ 225000)
         ) %>%
  pivot_wider(id_cols=PWSID,names_from=percentile,values_from=income_perc)
  
pws.income2 <-unnest(pws.income, cols = c(`20th Percentile`, `50th Percentile`, `NA`)) %>%
  select(PWSID,`20th Percentile`,`50th Percentile`) %>% distinct(.keep_all=TRUE)

aff <- left_join(bills,pws.income2,by=c("pwsid"="PWSID"))
aff$AR20 <- 12*100*aff$bill/aff$`20th Percentile`
aff$MHI <- 12*100*aff$bill/aff$`50th Percentile`
aff <- rename(aff,PWSID=pwsid)

aff <- left_join(aff,d.x,by="PWSID")
aff <- st_as_sf(aff)
aff <- distinct(aff,PWSID,`Water System Ownership`,hhsize,.keep_all=TRUE)
```

Urban-Rural-Income
```{r urbanrural}
d.ua <- st_join(d.x,st_transform(ua,3310), join=st_intersects, largest=TRUE)
d.ua$Pop.y[which(is.na(d.ua$Pop.y))]<-10
d.ua <- distinct(d.ua,PWSID,.keep_all=TRUE)
p<-ggplot(d.ua,aes(x=Pop.y,y=Pop.x, color=`Water System Ownership`)) +
  geom_point() +
  scale_x_log10() + scale_y_log10() + scale_color_viridis_d() + theme_dark() +
  xlab("Population of Urbanized Area") + ylab("Water System Service Population") +
  theme(legend.position=c(0.4,0.9))

png("Figures/Fig2.png")
p
dev.off()


inc <- left_join(pws.income2,d.ua,by="PWSID")
# p<-ggplot(inc,aes(x=Pop.y,y=`50th Percentile`, color=`Water System Ownership`, size=Pop.x/1000)) + scale_size_binned("Service Pop. (1000s)", trans="identity", breaks=c(1,10,100,1000,10000)) +
#   geom_point() +
#   scale_x_log10() + scale_y_log10() + scale_color_viridis_d(labels = function(x) str_wrap(x, width=13)) + theme_dark() +
#   xlab("Population of Urbanized Area") + ylab("Median Household Income within Service Area")

inc$cat <- "1. Pop. <1,000 (n=1753)"
inc$cat[which(inc$Pop.x>=1000)] <- "2. Pop. 1,000 - 10,000 (n=456)"
inc$cat[which(inc$Pop.x>=10000)] <- "3. Pop. 10,000 - 100,000 (n=326)"
inc$cat[which(inc$Pop.x>=100000)] <- "4. Pop. >= 100,000 (n=82)"

p<- ggplot(inc, aes(x=`50th Percentile`, color=`Water System Ownership`), size=4) +
  geom_density(lwd=1.24, adjust=2) + 
  scale_color_viridis_d(labels = function(x) str_wrap(x, width=13)) + 
  theme_dark() + scale_x_log10() +
  xlab("Median HH Income") + facet_wrap(vars(cat))

png("Figures/Fig3.png")
p
dev.off()

p<- ggplot(aff, aes(x=`50th Percentile`, color=`Water System Ownership`), size=4) +
  geom_density(lwd=2, adjust=2) + 
  scale_color_viridis_d(labels = function(x) str_wrap(x, width=13)) + 
  theme_dark() + scale_x_log10() +
  xlab("Median HH Income")

png("Figures/Fig3b.png")
p
dev.off()

```


Big map (urbanized areas and utilities)
```{r}
m3 <- mapview(d.x,zcol="Water System Ownership", alpha=0.8, layer.name = "All Water System Boundaries") +
  mapview(filter(aff,hhsize==4),stroke=TRUE,color="red",alpha.regions=0, layer.name = "Systems with price information", alpha = 0.5, col.regions="red")
mapshot(m3,"Figures/Map3.html")
```


SUmmarize ILI
```{r audit}
audit <- read_csv("Data/audit_corrected.csv")
audit <- audit %>% 
  rename(PWSID=pwsid,
         ILI=PI_INFRASTRUCT_LEAKAGE_INDEX) %>%
  group_by(PWSID)  %>%
  distinct(PWSID,REPORTING_YEAR,.keep_all = TRUE) %>%
  summarise(ILI=mean(ILI,na.rm=TRUE))

```

Summarize SDWA status
```{r, include=FALSE}
 
v <- read_csv("Data/SDWA_SERIOUS_VIOLATORS.csv")
v <- v%>% dplyr::select(PWSID,FISCAL_YEAR,SERIOUS_VIOLATOR,STATE) %>% filter(STATE=="CA")
v$count=1
v <- v%>%group_by(PWSID)%>%summarize(years_serious_violater=sum(count))

```

Summarize shutoffs
```{r}
shutoffs <- ear %>% filter(substr(QuestionName,1,12)=="WR SHUT_OFFS" & Year==2019)

pws_shutoff_collect <- shutoffs %>% filter(QuestionName=="WR SHUT_OFFS Once No Collect" & is.na(QuestionResults))

shutoffs_total <- shutoffs %>%
  filter(QuestionName=="WR SHUT_OFFS Once SF Total" |
           QuestionName=="WR SHUT_OFFS More Than Once SF Total" |
           QuestionName=="WR SHUT_OFFS More Than Once MF Total" |
           QuestionName=="WR SHUT_OFFS Once SF Total") %>%
  group_by(PWSID, Year) %>%
  summarise(shutoffs=sum(as.numeric(QuestionResults),na.rm=TRUE))%>%
  select(PWSID,shutoffs) %>%
  distinct(.keep_all=TRUE) %>% semi_join(pws_shutoff_collect,by="PWSID")
```

Summarize subsidies
```{r}

subsidies <- ear %>% 
  filter(QuestionName=="WR LL Subsidies") %>% 
  filter(QuestionResults!="-") %>% 
  select(PWSID,QuestionResults,Year) %>% 
  rename(subsidy=QuestionResults) %>% distinct(.keep_all=TRUE) 

subs <- subsidies %>% 
  group_by(PWSID) %>%
  mutate(maxYear=max(Year)) %>%
  ungroup() %>%
  filter(Year == maxYear)
```

# Descriptive Statistics and Plots

make big table
```{r}
D <- aff 

D <- left_join(D,audit,by="PWSID") # add ILI

D <- left_join(D,v,by="PWSID") #add SDWA violator status
  D$years_serious_violater[which(is.na(D$years_serious_violater))] <- 0

D <- left_join(D, shutoffs_total, by="PWSID") #add shutoffs_total  
D$shutoffs_perc = D$shutoffs/as.numeric(D$ServConn)

D <- left_join(D,subs,by="PWSID") ## add subsidy programs

save(D,"Data/FinalData.rds")
```

descriptive stats
```{r, results="asis"}
rm(list=ls())
load("Data/FinalData.rds")
D.f <- D
D <- D.f
D <- D %>% ungroup() %>% distinct(PWSID,hhsize,.keep_all = TRUE)

D1 <- D%>%filter(hhsize==1) 
D2 <- D%>%filter(hhsize==2) %>% select(PWSID,consumption,bill,AR20) %>% rename(consumption_2=consumption,
                                                                                      bill_hhsize2=bill, AR20_hhsize2 = AR20) %>% st_drop_geometry()
D3 <- D%>%filter(hhsize==3) %>% select(PWSID,consumption,bill,AR20) %>% rename(consumption_3=consumption,
                                                                                      bill_hhsize3=bill, AR20_hhsize3 = AR20)  %>% st_drop_geometry()
D4 <- D%>%filter(hhsize==4) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_4=consumption,
                                                                                      bill_hhsize4=bill, AR20_hhsize4 = AR20)  %>% st_drop_geometry()
D5 <- D%>%filter(hhsize==5) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_5=consumption,
                                                                                      bill_hhsize5=bill, AR20_hhsize5 = AR20) %>% st_drop_geometry()
D6 <- D%>%filter(hhsize==6) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_6=consumption,
                                                                                      bill_hhsize6=bill, AR20_hhsize6 = AR20) %>% st_drop_geometry()
D7 <- D%>%filter(hhsize==7) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_7=consumption,
                                                                                      bill_hhsize7=bill, AR20_hhsize7 = AR20) %>% st_drop_geometry()



D.wide <- D1 %>% 
  left_join(D2,by="PWSID") %>%
  left_join(D3,by="PWSID") %>%
  left_join(D4,by="PWSID") %>%
  left_join(D5,by="PWSID") %>%
  left_join(D6,by="PWSID") %>%
  left_join(D7,by="PWSID") 

D.wide$geometry <- NULL
library(psych)

D.wide <- filter(D.wide,!is.na(AR20))
D.wide2 <- D.wide %>% select(PWSID,Pop,`Water System Ownership`, 
                  `20th Percentile`, `50th Percentile`,
                 ILI, years_serious_violater, shutoffs_perc,subsidy,
                 bill_type,bill,bill_hhsize2,bill_hhsize3,bill_hhsize4,bill_hhsize5,bill_hhsize6,bill_hhsize7,
                 AR20,AR20_hhsize2,AR20_hhsize3,AR20_hhsize4,AR20_hhsize5,AR20_hhsize6,AR20_hhsize7)

D.wide2$bill_type[which(D.wide2$bill_type %in% c("1.49*usage_ccf","3.04*usage_ccf*1.333"))] <- "Uniform"

st(D.wide2, group='Water System Ownership', group.test=TRUE, digits=2)

D.wide3 <- filter(D.wide2,`Water System Ownership` %in% c("Local Government","Privately owned, PUC-regulated, for profit water company"))

st(D.wide3, group='Water System Ownership', group.test=TRUE, digits=2)
D.wide3$subsidy[which(is.na(D.wide3$subsidy))] <- "NA"

ggplot(filter(D.wide2,Pop>0), aes(x=Pop,y=AR20_hhsize4,color=`Water System Ownership`, shape=subsidy, cex=2))  + geom_hline(yintercept=3.5, color="green", lwd=2)+ geom_point(size=2) + scale_x_log10() + theme_dark() + scale_color_viridis_d() + theme(legend.position=c(0.7,0.6)) + xlab("Service Population (log10 scale)") + ylab("AR20 for 4-person Household")  # + geom_smooth(formula=y~log10(x),method='lm')

bounds <- sf::read_sf("https://opendata.arcgis.com/datasets/fbba842bf134497c9d611ad506ec48cc_0.geojson")
counties <- sf::read_sf("https://info.geoconnex.us/collections/counties/items?limit=10000&STATEFP=06")

inv <- read_excel("Data/EAR/inventory.xlsx",
                  sheet = "SDWISWaterSystemInventory071620") 

D.wide2 <- left_join(D.wide2,bounds,by="PWSID") 
D.wide3 <- left_join(D.wide3,bounds,by="PWSID") 
D.wide3 <- filter(Pop>0)

m1 <- felm(data=D.wide3,AR20_hhsize4 ~ as.factor(`Water System Ownership`) + log(Pop))

```
# Regression