---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(sf)
library(beeswarm)
library(knitr)
library(stargazer)
library(readxl)
library(mapview)
```

# Data Preperation

## Find utilities by ownership type

This is the inventory of all utilities that fill out the EAR
```{r inventory}
inv <- read_excel("Data/EAR/inventory.xlsx",
                  sheet = "SDWISWaterSystemInventory071620") %>% filter(WaterSystemType=="C")

bounds <- sf::read_sf("https://opendata.arcgis.com/datasets/fbba842bf134497c9d611ad506ec48cc_0.geojson")
```

We have to correct the rates data PWSIDs
```{r corrections}
rates <- readr::read_csv("Data/OWRS/summary_table_cleanedv2.csv")
corr <- read_csv("Data/OWRS/correction.csv")
rates <- left_join(rates,corr,by=c("utility_name"))
rates$pwsid.y <- NULL
rates <- rename(rates,pwsid=pwsid.x)
rates$pwsid[which(!is.na(rates$`corrected rates PWSID`))] <- rates$`corrected rates PWSID`[which(!is.na(rates$`corrected rates PWSID`))]
```

Now have to correct rate tier prices

```{r correct rates pwsis}
# merge in original bill units
original_units <- read_csv("Data/OWRS/summary_table.csv") %>% select(utility_name,bill_unit) 
rates <- left_join(rates,original_units,by="utility_name") 
#recalculate tier prices that were converted from ccf to kg with appropriate conversion factor dividing by 0.748052kgal/ccf to convert back to $/ccf, and then again to convert  to $/kgal. Original calculation was in a wrong unit of $/(ccf/0.748)
rates$Tier_price[which(rates$bill_unit.y=="ccf")]<-rates$Tier_price[which(rates$bill_unit.y=="ccf")]/(0.748052^2)
```
## Create Billing data
Now calculate prep to calculate water bills
```{r calculate bills}
# set values for non-discretionary water use
gpcd <- 50
days_month <- 365/12
hh_cons_person <- gpcd*days_month

#expand grid of all combinations of utility and household size (1-7)
names <- c(unique(rates$utility_name))
hhsize <- c(1:7)
hhsize <- expand.grid(hhsize,names)
names(hhsize) <- c("hhsize","utility_name")
hhsize$utility_name <- as.character(hhsize$utility_name)

#join to main table
rates <- left_join(rates,hhsize,by="utility_name")
rates$consumption <- (rates$hhsize * hh_cons_person)/1000
```

write function to calculate water bills
```{r bill_calculate}

rates <- arrange(rates,pwsid,utility_name,hhsize,Tier_number)
rates$Tier_volume[which(!is.na(rates$Tier_price) & is.na(rates$Tier_volume))] <- 10^10

rates <- rates %>% 
  group_by(utility_name,hhsize) %>%
  mutate(next_tier_volume = lead(Tier_volume),
         prev_tier_volume = case_when(
           Tier_number == 1 ~ 0,
           Tier_number > 1 ~ lag(Tier_volume)
         ),
         Tier_width = case_when(
           Tier_number == 1 & !is.na(next_tier_volume) ~ Tier_volume,
           Tier_number >1 ~ Tier_volume - prev_tier_volume,
           is.na(next_tier_volume) ~ 10^10,
           ),
         vol_in_tier = case_when(
           bill_type == "Uniform" & Tier_number ==1 ~ consumption,
           consumption <= prev_tier_volume ~ 0,
           consumption > Tier_volume ~ Tier_width,
           consumption > prev_tier_volume & consumption <= Tier_volume ~ consumption - prev_tier_volume#,
          # consumption > Tier_volume ~ Tier_width,
           #consumption >= Tier_volume & is.na(next_tier_volume) ~ consumption - Tier_volume#,
           #consumption >= Tier_volume & is.na(next_tier_volume) ~ consumption - Tier_volume
         )
  ) 

rates$vol_revenue <- NA
rates$vol_revenue = rates$Tier_price * rates$vol_in_tier

rates$vol_revenue[which(rates$bill_type=="1.49*usage_ccf")] <- 1.49*rates$consumption[which(rates$bill_type=="1.49*usage_ccf")]*0.748052
rates$vol_revenue[which(rates$bill_type=="3.04*usage_ccf*1.333")] <- 3.04*rates$consumption[which(rates$bill_type=="3.04*usage_ccf*1.333")]*1.333*0.748052

bills <- rates %>% group_by(pwsid,
                            utility_name,
                            bill_type,
                            hhsize,
                            consumption,
                            service_charge) %>%
  summarise(volumetric_charge = sum(vol_revenue,na.rm=TRUE))

bills$bill <- bills$service_charge + bills$volumetric_charge

```
Now we need to categorize them all by ownership type. To Recover ownership type, we read in the latest EAR
```{r type}
# ear13 <- read_tsv("Data/EAR/earsurveyresults_2013ry.zip",col_types="ccdcccdddc")
#  ear14 <- read_tsv("Data/EAR/earsurveyresults_2014ry.zip",col_types="ccdcccdddc")
#  ear15 <- read_tsv("Data/EAR/earsurveyresults_2015ry.zip",col_types="ccdcccdddc")
#  ear16 <- read_tsv("Data/EAR/earsurveyresults_2016ry.zip",col_types="ccdcccdddc")
#  ear17 <- read_tsv("Data/EAR/earsurveyresults_2017ry.zip",col_types="ccdcccdddc")
#  ear18 <- read_tsv("Data/EAR/earsurveyresults_2018ry.zip",col_types="ccdcccdddc")
#  ear19 <- read_tsv("Data/EAR/earsurveyresults_2019ry.zip",col_names=c("PWSID",
#                                                                       "Survey",
#                                                                       "Year",
#                                                                       "SectionName",
#                                                                       "QuestionName",
#                                                                       "QuestionResults",
#                                                                       "SurveyID",
#                                                                       "SectionID",
#                                                                       "QuestionID",
#                                                                       "Pk"), col_types="ccdcccdddc")
# ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18,ear19)
# save(ear,file="Data/ear.rds")
load("Data/ear.rds")
ownership <- ear %>% filter(QuestionName %in% c("Water System Ownership",
                                    "IsWholesaler")) %>% 
  select(PWSID, 
         Year, 
         QuestionName, 
         QuestionResults,
         QuestionID,
         Pk) %>% 
  pivot_wider(id_cols = c(PWSID, Year),
              names_from = QuestionName,
              values_from = QuestionResults,
              names_repair="unique") %>% unnest(cols=c("Water System Ownership","IsWholesaler") ) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(`Water System Ownership` %in% c(
    "Privately owned business (non-community)",
    "Privately owned Mutual Water Company or Association",
    "Privately owned, non-PUC-regulated (Community Water System)",
    "Local Government",
    "Privately owned, PUC-regulated, for profit water company"
    
  )) 

```
## Census data

Get all the variables
```{r census_cars}
census_api_key("b25f8b1b7bf10561c9cbc3a20a4d2572677f1f05")
options(tigris_use_cache = TRUE)
vars <- load_variables(2019, "acs5", cache = TRUE)
census_vars2 <- c(median_income="B19013_001",
                 pop_in_hh_with_income_assistance="B09010_002",
                 pop_in_hh_with_no_income_assistance="B09010_008",
                 hh_inc_5k="B19001_002",
                 hh_inc_12.5k="B19001_003",
                 hh_inc_17.5k="B19001_004",
                 hh_inc_22.5k="B19001_005",
                 hh_inc_27.5k="B19001_006",
                 hh_inc_32.5k="B19001_007",
                 hh_inc_37.5k="B19001_008",
                 hh_inc_42.5k="B19001_009",
                 hh_inc_47.5k="B19001_010",
                 hh_inc_55k="B19001_011",
                 hh_inc_67.5k="B19001_012",
                 hh_inc_87.5k="B19001_013",
                 hh_inc_112.5k="B19001_014",
                 hh_inc_137.5k="B19001_015",
                 hh_inc_175k="B19001_016",
                 hh_inc_gr200k="B19001_017",
                 hh_income_count = "B19001_001")

```

Lets get all the Municipal boundaries
```{r}
st <- get_acs(year=2019,geography = "state",
                  variables = "B01003_001", geometry = TRUE) %>% filter(NAME=="California")
pl <- get_acs(year=2019,geography = "place",
                  variables = "B01003_001", geometry = TRUE, state= "CA") 

vars <- load_variables(2019, "acs5", cache = TRUE)
```

Let's get all the Census Block Groups
```{r}
bg <- get_acs(year=2019,geography = "block group",
                  variables = census_vars2, geometry = TRUE, state= "CA") 
save(bg, file="Data/census_blockgroups.rds")
```

Let's get all the Urbanized Areas and combine them into super areas.
```{r}
ua <- get_acs(year=2019,geography = "urban area",
                  variables = c("B01003_001","B19013_001"), geometry = TRUE, output="wide")
ua<-rename(ua,Pop=B01003_001E)
ua <- ua[st,]
ua2 <- st_as_sf(rgeos::gUnaryUnion(as_Spatial(ua)))
ua2 <- select(ua,Pop)
ua3 <- st_union(ua)
ua4 <- aggregate(ua2,ua3,FUN=sum, join=st_intersects)
```

## Descriptive stats
Now we categorize all utilities in the SDWIS Inventory by type
```{r merge_type}
own <- ownership %>% group_by(PWSID,`Water System Ownership`) %>% add_tally() %>% ungroup() %>% group_by(PWSID) %>% add_tally() %>% ungroup()
own1 <- filter(own,n == nn)
own1 <- distinct(own,PWSID,.keep_all=TRUE)
own2 <- filter(own, n != nn)
own2 <- own2 %>% 
  distinct(PWSID, `Water System Ownership`, .keep_all=TRUE) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(Year==maxYear) %>% 
  group_by(PWSID) %>%
  add_tally()

own1 <- select(own1, PWSID, `Water System Ownership`,Year)
own2 <- select(own2, PWSID, `Water System Ownership`,Year)
own <- bind_rows(own1,own2)
own <- own %>% group_by(PWSID) %>% mutate(maxYear=max(Year)) %>% ungroup() %>% filter(Year == maxYear)

rm(own1,own2)


d <- left_join(inv,own, by="PWSID")
d <- select(d, PWSID, PWS_Name, County, Pop, ServConn, `Water System Ownership`)
d$log10PopCat <- floor(log10(d$Pop))

```

## some distributive plots
```{r, results='asis'}
d <- filter(d,`Water System Ownership` != "Privately owned business (non-community)")
x <- data.frame(table(d$log10PopCat,d$`Water System Ownership`))
x <- x%>%pivot_wider(id_cols = Var1,names_from = Var2, values_from=Freq)

datatable(x,extensions="Buttons",options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv')))



y <- d %>% 
  mutate(TotPop = sum(Pop,na.rm=TRUE),
         PropPop = Pop/TotPop) %>%
  group_by(log10PopCat,`Water System Ownership`) %>% 
  summarise(Population = sum(Pop,na.rm=TRUE),
            Pop_percent = 100*sum(PropPop,na.rm=TRUE)) %>%
  pivot_wider(id_cols = `log10PopCat`, 
              names_from = `Water System Ownership`,
              values_from = c(Population,Pop_percent))

datatable(y,extensions="Buttons",options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv')))

p<- ggplot(d, aes(x=log10(Pop), color=`Water System Ownership`)) +
  geom_density() + 
  scale_color_viridis_d() + 
  theme_dark() + 
  theme(legend.position=c(0.69, 0.85)) +
  xlab("log(base 10) of Service Population")

p
```

```{r, include=FALSE}
 
 ear19 <- read_tsv("Data/EAR/earsurveyresults_2019ry.zip",col_types="ccdcccdddc")
 
 ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18,ear19)
 rm(ear13,ear14,ear15,ear16,ear17,ear18,ear19)
 save(ear,file="Data/EAR/ear.rds")
#load("Data/EAR/ear.rds")
```



# Descriptive Statistics and Plots

# Regression