---
title: "Documentation"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(sf)
library(beeswarm)
library(knitr)
library(stargazer)
library(readxl)
library(mapview)
library(viridis)
library(DT)
library(scales)
library(vtable)
library(lfe)
library(ggpubr)
library(dineq)
library(easyGgplot2)

mapviewPWS <- function(pwsid,...){
  url <- paste0("https://geoconnex.us/ref/pws/",pwsid)
  pws <- sf::read_sf(url)
  mapview::mapview(pws,...)
}

mapviewOptions(fgb=FALSE)
```


# Data Preperation

## Find utilities by ownership type

This is the inventory of all utilities that fill out the EAR
```{r inventory}
inv <- read_excel("Data/EAR/inventory.xlsx",
                  sheet = "SDWISWaterSystemInventory071620") %>% filter(WaterSystemType=="C")


sdwis <- read_csv("https://data.epa.gov/efservice/SERVICE_AREA/PRIMACY_AGENCY_CODE/CA/EXCEL")

bounds <- sf::read_sf("https://opendata.arcgis.com/datasets/fbba842bf134497c9d611ad506ec48cc_0.geojson")
```

We have to correct the rates data PWSIDs
```{r corrections}
rates <- readr::read_csv("Data/OWRS/summary_table_cleanedv2.csv")
corr <- read_csv("Data/OWRS/correction.csv")
rates <- left_join(rates,corr,by=c("utility_name"))
rates$pwsid.y <- NULL
rates <- rename(rates,pwsid=pwsid.x)
rates$pwsid[which(!is.na(rates$`corrected rates PWSID`))] <- rates$`corrected rates PWSID`[which(!is.na(rates$`corrected rates PWSID`))]
```

Now have to correct rate tier prices

```{r correct rates pwsis}
# merge in original bill units
original_units <- read_csv("Data/OWRS/summary_table.csv") %>% select(utility_name,bill_unit) 
rates <- left_join(rates,original_units,by="utility_name") 
#recalculate tier prices that were converted from ccf to kg with appropriate conversion factor dividing by 0.748052kgal/ccf to convert back to $/ccf, and then again to convert  to $/kgal. Original calculation was in a wrong unit of $/(ccf/0.748)
rates$Tier_price[which(rates$bill_unit.y=="ccf")]<-rates$Tier_price[which(rates$bill_unit.y=="ccf")]/(0.748052^2)
```
## Create Billing data
Now calculate prep to calculate water bills
```{r calculate bills}
# set values for non-discretionary water use
gpcd <- 50
days_month <- 365/12
hh_cons_person <- gpcd*days_month

#expand grid of all combinations of utility and household size (1-7)
names <- c(unique(rates$utility_name))
hhsize <- c(1:7)
hhsize <- expand.grid(hhsize,names)
names(hhsize) <- c("hhsize","utility_name")
hhsize$utility_name <- as.character(hhsize$utility_name)

#join to main table
rates <- left_join(rates,hhsize,by="utility_name")
rates$consumption <- (rates$hhsize * hh_cons_person)/1000
```

write function to calculate water bills
```{r bill_calculate}

rates <- arrange(rates,pwsid,utility_name,hhsize,Tier_number)
rates$Tier_volume[which(!is.na(rates$Tier_price) & is.na(rates$Tier_volume))] <- 10^10

rates <- rates %>% 
  group_by(utility_name,hhsize) %>%
  mutate(next_tier_volume = lead(Tier_volume),
         prev_tier_volume = case_when(
           Tier_number == 1 ~ 0,
           Tier_number > 1 ~ lag(Tier_volume)
         ),
         Tier_width = case_when(
           Tier_number == 1 & !is.na(next_tier_volume) ~ Tier_volume,
           Tier_number >1 ~ Tier_volume - prev_tier_volume,
           is.na(next_tier_volume) ~ 10^10,
           ),
         vol_in_tier = case_when(
           bill_type == "Uniform" & Tier_number ==1 ~ consumption,
           consumption <= prev_tier_volume ~ 0,
           consumption > Tier_volume ~ Tier_width,
           consumption > prev_tier_volume & consumption <= Tier_volume ~ consumption - prev_tier_volume#,
          # consumption > Tier_volume ~ Tier_width,
           #consumption >= Tier_volume & is.na(next_tier_volume) ~ consumption - Tier_volume#,
           #consumption >= Tier_volume & is.na(next_tier_volume) ~ consumption - Tier_volume
         )
  ) 

rates$vol_revenue <- NA
rates$vol_revenue = rates$Tier_price * rates$vol_in_tier

rates$vol_revenue[which(rates$bill_type=="1.49*usage_ccf")] <- 1.49*rates$consumption[which(rates$bill_type=="1.49*usage_ccf")]*0.748052
rates$vol_revenue[which(rates$bill_type=="3.04*usage_ccf*1.333")] <- 3.04*rates$consumption[which(rates$bill_type=="3.04*usage_ccf*1.333")]*1.333*0.748052

bills <- rates %>% group_by(pwsid,
                            utility_name,
                            bill_type,
                            hhsize,
                            consumption,
                            service_charge) %>%
  summarise(volumetric_charge = sum(vol_revenue,na.rm=TRUE))

bills$bill <- bills$service_charge + bills$volumetric_charge

```
Now we need to categorize them all by ownership type. To Recover ownership type, we read in the latest EAR
```{r, type}
# ear13 <- read_tsv("Data/EAR/earsurveyresults_2013ry.zip",col_types="ccdcccdddc")
#  ear14 <- read_tsv("Data/EAR/earsurveyresults_2014ry.zip",col_types="ccdcccdddc")
#  ear15 <- read_tsv("Data/EAR/earsurveyresults_2015ry.zip",col_types="ccdcccdddc")
#  ear16 <- read_tsv("Data/EAR/earsurveyresults_2016ry.zip",col_types="ccdcccdddc")
#  ear17 <- read_tsv("Data/EAR/earsurveyresults_2017ry.zip",col_types="ccdcccdddc")
#  ear18 <- read_tsv("Data/EAR/earsurveyresults_2018ry.zip",col_types="ccdcccdddc")
#  ear19 <- read_tsv("Data/EAR/earsurveyresults_2019ry.zip",col_names=c("PWSID",
#                                                                       "Survey",
#                                                                       "Year",
#                                                                       "SectionName",
#                                                                       "QuestionName",
#                                                                       "QuestionResults",
#                                                                       "SurveyID",
#                                                                       "SectionID",
#                                                                       "QuestionID",
#                                                                       "Pk"), col_types="ccdcccdddc")
# ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18,ear19)
# save(ear,file="Data/ear.rds")
load("Data/ear.rds")
ownership <- ear %>% filter(QuestionName %in% c("Water System Ownership",
                                    "IsWholesaler")) %>% 
  select(PWSID, 
         Year, 
         QuestionName, 
         QuestionResults,
         QuestionID,
         Pk) %>% 
  pivot_wider(id_cols = c(PWSID, Year),
              names_from = QuestionName,
              values_from = QuestionResults,
              names_repair="unique") %>% unnest(cols=c("Water System Ownership","IsWholesaler") ) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(`Water System Ownership` %in% c(
    "Privately owned business (non-community)",
    "Privately owned Mutual Water Company or Association",
    "Privately owned, non-PUC-regulated (Community Water System)",
    "Local Government",
    "Privately owned, PUC-regulated, for profit water company"
    
  )) 

own <- ownership %>% group_by(PWSID,`Water System Ownership`) %>% add_tally() %>% ungroup() %>% group_by(PWSID) %>% add_tally() %>% ungroup()
own1 <- filter(own,n == nn)
own1 <- distinct(own,PWSID,.keep_all=TRUE)
own2 <- filter(own, n != nn)
own2 <- own2 %>% 
  distinct(PWSID, `Water System Ownership`, .keep_all=TRUE) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(Year==maxYear) %>% 
  group_by(PWSID) %>%
  add_tally()

own1 <- select(own1, PWSID, `Water System Ownership`,Year)
own2 <- select(own2, PWSID, `Water System Ownership`,Year)
own <- bind_rows(own1,own2)
own <- own %>% group_by(PWSID) %>% mutate(maxYear=max(Year)) %>% ungroup() %>% filter(Year == maxYear)

rm(own1,own2)
# 
# ownership2 <- ownership left_join(ownership, sdwis,by=c("PWSID" = "SERVICE_AREA.PWSID"))

own2 <- own %>% left_join(sdwis,by=c("PWSID" = "SERVICE_AREA.PWSID"))
own2$SERVICE_AREA.IS_PRIMARY_SERVICE_AREA_CODE[which(is.na(own2$SERVICE_AREA.IS_PRIMARY_SERVICE_AREA_CODE))] <- "N"

own <- own2 %>% filter(SERVICE_AREA.SERVICE_AREA_TYPE_CODE %in% c("HA","MH","MU","OA","ON","OR","RA","SR","SU") & SERVICE_AREA.IS_PRIMARY_SERVICE_AREA_CODE == "Y")

own_d <- left_join(inv,own,by="PWSID")
```
## Census data

Get all the variables
```{r, include=FALSE}
census_api_key("b25f8b1b7bf10561c9cbc3a20a4d2572677f1f05")
```
```{r, census_cars}
options(tigris_use_cache = TRUE)
vars <- load_variables(2019, "acs5", cache = TRUE)
census_vars2 <- c(median_income="B19013_001",
                 pop_in_hh_with_income_assistance="B09010_002",
                 pop_in_hh_with_no_income_assistance="B09010_008",
                 hh_inc_5k="B19001_002",
                 hh_inc_12.5k="B19001_003",
                 hh_inc_17.5k="B19001_004",
                 hh_inc_22.5k="B19001_005",
                 hh_inc_27.5k="B19001_006",
                 hh_inc_32.5k="B19001_007",
                 hh_inc_37.5k="B19001_008",
                 hh_inc_42.5k="B19001_009",
                 hh_inc_47.5k="B19001_010",
                 hh_inc_55k="B19001_011",
                 hh_inc_67.5k="B19001_012",
                 hh_inc_87.5k="B19001_013",
                 hh_inc_112.5k="B19001_014",
                 hh_inc_137.5k="B19001_015",
                 hh_inc_175k="B19001_016",
                 hh_inc_gr200k="B19001_017",
                 hh_income_count = "B19001_001",
                 QUL1 = "B19080_001",
                 QUL2 = "B19080_002",
                 QUL3 = "B19080_003",
                 QUL4 = "B19080_004",
                 pop_pov = "C17002_001",
                 pop_gr_200FPL = "C17002_008" 
                 )

```

Lets get all the Municipal boundaries
```{r}
st <- get_acs(year=2019,geography = "state",
                  variables = "B01003_001", geometry = TRUE) %>% filter(NAME=="California")
pl <- get_acs(year=2019,geography = "place",
                  variables = census_vars2, geometry = TRUE, state= "CA") 

vars <- load_variables(2019, "acs5", cache = TRUE)
```

Let's get all the Census Block Groups
```{r}
 bg <- get_acs(year=2019,geography = "block group",
                   variables = census_vars2, geometry = TRUE, state= "CA") 
 save(bg, file="Data/census_blockgroups.rds")
load("Data/census_blockgroups.rds")
```

Let's get all the Urbanized Areas and combine them into super areas.
```{r}
ua <- get_acs(year=2019,geography = "urban area",
                  variables = c("B01003_001","B19013_001"), geometry = TRUE, output="wide")
ua<-rename(ua,Pop=B01003_001E)
ua <- ua[st,]
```

## Descriptive stats
Now we categorize all utilities in the SDWIS Inventory by type
```{r, merge_type}
own <- ownership %>% group_by(PWSID,`Water System Ownership`) %>% add_tally() %>% ungroup() %>% group_by(PWSID) %>% add_tally() %>% ungroup()
own1 <- filter(own,n == nn)
own1 <- distinct(own,PWSID,.keep_all=TRUE)
own2 <- filter(own, n != nn)
own2 <- own2 %>% 
  distinct(PWSID, `Water System Ownership`, .keep_all=TRUE) %>%
  group_by(PWSID) %>%
  mutate(maxYear = max(Year)) %>%
  ungroup() %>%
  filter(Year==maxYear) %>% 
  group_by(PWSID) %>%
  add_tally()

own1 <- select(own1, PWSID, `Water System Ownership`,Year)
own2 <- select(own2, PWSID, `Water System Ownership`,Year)
own <- bind_rows(own1,own2)
own <- own %>% group_by(PWSID) %>% mutate(maxYear=max(Year)) %>% ungroup() %>% filter(Year == maxYear)

rm(own1,own2)


d <- left_join(inv,own, by="PWSID")
d <- select(d, PWSID, PWS_Name, County, Pop, ServConn, `Water System Ownership`)
d$log10PopCat <- floor(log10(d$Pop))

```

## some distributive plots
```{r, results='asis'}
d <- filter(d,`Water System Ownership` != "Privately owned business (non-community)")
x <- data.frame(table(d$log10PopCat,d$`Water System Ownership`))
x <- x%>%pivot_wider(id_cols = Var1,names_from = Var2, values_from=Freq)

datatable(x,extensions="Buttons",options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv')))



y <- d %>% 
  mutate(TotPop = sum(Pop,na.rm=TRUE),
         PropPop = Pop/TotPop) %>%
  group_by(log10PopCat,`Water System Ownership`) %>% 
  summarise(Population = sum(Pop,na.rm=TRUE),
            Pop_percent = 100*sum(PropPop,na.rm=TRUE)) %>%
  pivot_wider(id_cols = `log10PopCat`, 
              names_from = `Water System Ownership`,
              values_from = c(Population,Pop_percent))

datatable(y,extensions="Buttons",options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv')))

p<- ggplot(d, aes(x=log10(Pop), color=`Water System Ownership`), size=4) +
  geom_density(lwd=2) + 
  scale_color_viridis_d() + 
  theme_dark() + 
  theme(legend.position=c(0.69, 0.85)) +
  xlab("log(base 10) of Service Population")

p
```
Spatial demonstration figure. Show utility boundaries, municipal boundaries, and censusblock groups
```{r}
b <- bounds %>% select(SABL_PWSID)  %>% rename(PWSID=SABL_PWSID)
#d.b <- d %>% inner_join(b,by="PWSID") %>% st_as_sf()
d.b <- own_d %>% inner_join(b,by="PWSID") %>% st_as_sf()
pal <- magma(n = length(unique(pl$NAME)), direction = -1)

bkfield <- st_transform(filter(ua,GEOID=="04681"),4326)
d1 <- d.b[bkfield,,op=st_intersects]
pl1 <- st_transform(pl,4326)[bkfield,,op=st_intersects]

m <-  mapview(pl1,
              stroke=TRUE,
              color="red",
              alpha.regions=0,
              layer.name = "Municipal Boundaries",
              lwd=2,legend=TRUE,col.regions="red") + 
  mapview(d1,
          zcol="Water System Ownership",
          alpha=0.8, layer.name = "Water System Boundaries") 
mapshot(m,"Figures/Map1.html")
m

d.x <- st_buffer(st_transform(d.b,3310),dist=0)

```
```{r, include=FALSE}

bg.x <- bg %>% filter(variable=="median_income") %>%
  select(GEOID,NAME,estimate,geometry) %>% rename(median_income = estimate) %>%
  st_transform(3310) %>%
  st_buffer(dist=0) %>%
  mutate(AreaBlockGroup = st_area(.))

d.x$AreaPWS <- st_area(d.x)


bg.bounds <- st_intersection(d.x,bg.x) 
bg.bounds <- bg.bounds %>% group_by(PWSID) %>% add_tally()
```

Bakersfield example 
```{r, example, results="asis"}
bkfield <- filter(ua,GEOID=="04681")
bg.bounds <- st_transform(bg.bounds,4326)
bkfield <- st_transform(bkfield,4326)
bkfield <- bg.bounds[bkfield,]

bk.bound <- d.b[bkfield,,op=st_intersects]

m2<-mapview(bkfield,zcol="median_income",layer.name="Census Block Group - Median HH Income") + mapview(bk.bound, alpha=1, layer.name = "Water System Boundaries", stroke=TRUE,color="black",col.regions="black", alpha.regions=0, lwd=4,legend=TRUE)
m2
#mapshot(m2,"Figures/Map2.html")
```


Calculate affordability
```{r, calcualte_affordability}
bg.bounds <- st_transform(bg.bounds,3310)
bg.bounds$Area_BlockGroupPWS <- st_area(bg.bounds)
bg.bounds$Percent_BlockGroupinPWS <- bg.bounds$Area_BlockGroupPWS/bg.bounds$AreaBlockGroup
bg.bounds$PercentPWS_inBlockGroup <- bg.bounds$Area_BlockGroupPWS/bg.bounds$AreaPWS
small <- filter(bg.bounds,(as.numeric(PercentPWS_inBlockGroup)==1 & n==1 & AreaPWS<0.5*AreaBlockGroup))

pws.income.try2 <- bg.bounds %>% st_drop_geometry() %>%
  left_join(bg,by="GEOID") %>%
  filter(variable %in% c('hh_inc_5k',
                 'hh_inc_12.5k',
                 'hh_inc_17.5k',
                 'hh_inc_22.5k',
                 'hh_inc_27.5k',
                 'hh_inc_32.5k',
                 'hh_inc_37.5k',
                 'hh_inc_42.5k',
                 'hh_inc_47.5k',
                 'hh_inc_55k',
                 'hh_inc_67.5k',
                 'hh_inc_87.5k',
                 'hh_inc_112.5k',
                 'hh_inc_137.5k',
                 'hh_inc_175k',
                 'hh_inc_gr200k')) %>%
  mutate(weighted_count = estimate*Percent_BlockGroupinPWS) %>%
  group_by(PWSID,variable) %>%
  summarise(estimate=sum(weighted_count)) %>% 
  ungroup()

  pws.income <- pws.income.try2 %>% group_by(PWSID) %>% filter(sum(as.numeric(estimate))>0) %>% ungroup() %>%
  mutate(order=case_when(variable=="hh_inc_5k" ~ 1,
                 variable=="hh_inc_12.5k" ~ 2,
                 variable=="hh_inc_17.5k" ~ 3,
                 variable=="hh_inc_22.5k" ~ 4,
                 variable=="hh_inc_27.5k" ~ 5,
                 variable=="hh_inc_32.5k" ~ 6,
                 variable=="hh_inc_37.5k" ~ 7,
                 variable=="hh_inc_42.5k" ~ 8,
                 variable=="hh_inc_47.5k" ~ 9,
                 variable=="hh_inc_55k" ~ 10,
                 variable=="hh_inc_67.5k" ~ 11,
                 variable=="hh_inc_87.5k" ~ 12,
                 variable=="hh_inc_112.5k" ~ 13,
                 variable=="hh_inc_137.5k" ~ 14,
                 variable=="hh_inc_175k" ~ 15,
                 variable=="hh_inc_gr200k" ~ 16),
         upper_limit=case_when(variable=="hh_inc_5k" ~ 10000,
                 variable=="hh_inc_12.5k" ~ 15000,
                 variable=="hh_inc_17.5k" ~ 20000,
                 variable=="hh_inc_22.5k" ~ 25000,
                 variable=="hh_inc_27.5k" ~ 30000,
                 variable=="hh_inc_32.5k" ~ 35000,
                 variable=="hh_inc_37.5k" ~ 40000,
                 variable=="hh_inc_42.5k" ~ 45000,
                 variable=="hh_inc_47.5k" ~ 50000,
                 variable=="hh_inc_55k" ~ 60000,
                 variable=="hh_inc_67.5k" ~ 75000,
                 variable=="hh_inc_87.5k" ~ 100000,
                 variable=="hh_inc_112.5k" ~ 125000,
                 variable=="hh_inc_137.5k" ~ 150000,
                 variable=="hh_inc_175k" ~ 200000,
                 variable=="hh_inc_gr200k" ~ 300000),
         midpoint=case_when(variable=="hh_inc_5k" ~ 5000,
                 variable=="hh_inc_12.5k" ~ 12500,
                 variable=="hh_inc_17.5k" ~ 17500,
                 variable=="hh_inc_22.5k" ~ 22500,
                 variable=="hh_inc_27.5k" ~ 27500,
                 variable=="hh_inc_32.5k" ~ 32500,
                 variable=="hh_inc_37.5k" ~ 37500,
                 variable=="hh_inc_42.5k" ~ 42500,
                 variable=="hh_inc_47.5k" ~ 47500,
                 variable=="hh_inc_55k" ~ 55000,
                 variable=="hh_inc_67.5k" ~ 67500,
                 variable=="hh_inc_87.5k" ~ 87500,
                 variable=="hh_inc_112.5k" ~ 112500,
                 variable=="hh_inc_137.5k" ~ 137500,
                 variable=="hh_inc_175k" ~ 175000,
                 variable=="hh_inc_gr200k" ~ 250000)) %>%
  arrange(PWSID,order) %>% 
    group_by(PWSID) %>%
     mutate(estimate= as.numeric(estimate),
     cum_inc_sum = as.numeric(cumsum(estimate)),
          percentile_inc = 100*cum_inc_sum/sum(estimate),
       median_perc = 50,
       lower_perc = 20) %>%
   mutate(income50 = approx(x = percentile_inc, y = upper_limit, xout = median_perc)$y,
          income20 = approx(x = percentile_inc, y = upper_limit, xout = lower_perc)$y,
          gini = gini.wtd(x = midpoint, weights = estimate)) 
   
    pws.income <- pws.income %>% ungroup() %>%
    dplyr::select(PWSID, income20, income50, gini) %>%
    distinct(.keep_all=TRUE)
    
    pws.income$income20[which(is.na(pws.income$income20))] <- runif(length(pws.income$income20[which(is.na(pws.income$income20))]),min=0,max=10000)
# 
# pws.income <- bg.bounds %>% st_drop_geometry() %>%
#   left_join(bg,by="GEOID") %>%
#   filter(variable %in% c('hh_inc_5k',
#                  'hh_inc_12.5k',
#                  'hh_inc_17.5k',
#                  'hh_inc_22.5k',
#                  'hh_inc_27.5k',
#                  'hh_inc_32.5k',
#                  'hh_inc_37.5k',
#                  'hh_inc_42.5k',
#                  'hh_inc_47.5k',
#                  'hh_inc_55k',
#                  'hh_inc_67.5k',
#                  'hh_inc_87.5k',
#                  'hh_inc_112.5k',
#                  'hh_inc_137.5k',
#                  'hh_inc_175k',
#                  'hh_inc_gr200k')) %>%
#   group_by(PWSID,variable) %>%
#   summarise(estimate=sum(estimate*Percent_BlockGroupinPWS)) %>% 
#   ungroup() %>%
#   mutate(var2=case_when(variable=="hh_inc_5k" ~ 10,
#                  variable=="hh_inc_12.5k" ~ 2,
#                  variable=="hh_inc_17.5k" ~ 3,
#                  variable=="hh_inc_22.5k" ~ 4,
#                  variable=="hh_inc_27.5k" ~ 5,
#                  variable=="hh_inc_32.5k" ~ 6,
#                  variable=="hh_inc_37.5k" ~ 7,
#                  variable=="hh_inc_42.5k" ~ 8,
#                  variable=="hh_inc_47.5k" ~ 9,
#                  variable=="hh_inc_55k" ~ 10,
#                  variable=="hh_inc_67.5k" ~ 11,
#                  variable=="hh_inc_87.5k" ~ 12,
#                  variable=="hh_inc_112.5k" ~ 13,
#                  variable=="hh_inc_137.5k" ~ 14,
#                  variable=="hh_inc_175k" ~ 15,
#                  variable=="hh_inc_gr200k" ~ 16,)) %>% 
#   arrange(PWSID,var2) %>% 
#   group_by(PWSID) %>%
#   mutate(cum_inc_sum = cumsum(estimate),
#          percentile_inc = 100*cum_inc_sum/sum(estimate)) %>%
#   ungroup() %>%
#   mutate(perc_dist20=abs(as.numeric(percentile_inc)-20),
#          perc_dist50=abs(as.numeric(percentile_inc)-50)) %>%
#   group_by(PWSID) %>%
#   filter(perc_dist20==min(perc_dist20) | 
#          perc_dist50==min(perc_dist50)) %>%
#   mutate(percentile=case_when(var2==min(var2)~"20th Percentile",
#                               var2==max(var2)~"50th Percentile"),
#          income_perc=case_when(var2==1 ~ 5000,
#                                var2==2 ~ 12500,
#                                var2==3 ~ 17500,
#                                var2==4 ~ 22500,
#                                var2==5 ~ 27500,
#                                var2==6 ~ 32500,
#                                var2==7 ~ 37500,
#                                var2==8 ~ 42500,
#                                var2==9 ~ 47500,
#                                var2==10 ~ 55000,
#                                var2==11 ~ 67500,
#                                var2==12 ~ 87500,
#                                var2==13 ~ 112500,
#                                var2==14 ~ 137500,
#                                var2==15 ~ 175000,
#                                var2==16 ~ 225000)
#          ) %>%
#   pivot_wider(id_cols=PWSID,names_from=percentile,values_from=income_perc)
    
    pws.fpl <- bg.bounds %>% st_drop_geometry() %>%
  left_join(bg,by="GEOID") %>%
  filter(variable %in% c('pop_pov','pop_gr_200FPL')) %>%
  mutate(weighted_count = estimate*Percent_BlockGroupinPWS) %>%
  group_by(PWSID,variable) %>%
  summarise(estimate=as.numeric(sum(weighted_count))) %>% ungroup() %>%
      pivot_wider(id_cols=PWSID,names_from=variable,values_from=estimate) %>% mutate(perc_below_200FPL = 100*(pop_pov - pop_gr_200FPL)/pop_pov)
  
pws.income2 <- left_join(pws.income,pws.fpl,by="PWSID")
aff <- left_join(bills,pws.income2,by=c("pwsid"="PWSID"))
aff$AR20 <- 12*100*aff$bill/aff$`20th Percentile`
aff$MHI <- 12*100*aff$bill/aff$`50th Percentile`
aff <- rename(aff,PWSID=pwsid)

aff <- left_join(aff,d.x,by="PWSID")
aff <- st_as_sf(aff)
aff <- distinct(aff,PWSID,`Water System Ownership`,hhsize,.keep_all=TRUE)
```

Urban-Rural-Income
```{r, urbanrural}
d.ua <- st_join(d.x,st_transform(ua,3310), join=st_intersects, largest=TRUE)
d.ua$Pop.y[which(is.na(d.ua$Pop.y))]<-10
d.ua <- distinct(d.ua,PWSID,.keep_all=TRUE)
p<-ggplot(d.ua,aes(x=Pop.y,y=Pop.x, color=`Water System Ownership`)) +
  geom_point() +
  scale_x_log10() + scale_y_log10() + scale_color_viridis_d() + theme_dark() +
  xlab("Population of Urbanized Area") + ylab("Water System Service Population") +
  theme(legend.position=c(0.4,0.9))

png("Figures/Fig2.png")
p
dev.off()
p

inc <- left_join(pws.income2,d.ua,by="PWSID")
# p<-ggplot(inc,aes(x=Pop.y,y=`50th Percentile`, color=`Water System Ownership`, size=Pop.x/1000)) + scale_size_binned("Service Pop. (1000s)", trans="identity", breaks=c(1,10,100,1000,10000)) +
#   geom_point() +
#   scale_x_log10() + scale_y_log10() + scale_color_viridis_d(labels = function(x) str_wrap(x, width=13)) + theme_dark() +
#   xlab("Population of Urbanized Area") + ylab("Median Household Income within Service Area")

inc$cat <- "1. Pop. <1,000 (n=1753)"
inc$cat[which(inc$Pop.x>=1000)] <- "2. Pop. 1,000 - 10,000 (n=456)"
inc$cat[which(inc$Pop.x>=10000)] <- "3. Pop. 10,000 - 100,000 (n=326)"
inc$cat[which(inc$Pop.x>=100000)] <- "4. Pop. >= 100,000 (n=82)"

p<- ggplot(inc, aes(x=`50th Percentile`, color=`Water System Ownership`), size=4) +
  geom_density(lwd=1.24, adjust=2) + 
  scale_color_viridis_d(labels = function(x) str_wrap(x, width=13)) + 
  theme_dark() + scale_x_log10() +
  xlab("Median HH Income") + facet_wrap(vars(cat))

png("Figures/Fig3.png")
p
dev.off()
p


p<- ggplot(aff, aes(x=`50th Percentile`, color=`Water System Ownership`), size=4) +
  geom_density(lwd=2, adjust=2) + 
  scale_color_viridis_d(labels = function(x) str_wrap(x, width=13)) + 
  theme_dark() + scale_x_log10() +
  xlab("Median HH Income")

png("Figures/Fig3b.png")
p
dev.off()

p



```


Big map (urbanized areas and utilities)
```{r}
m3 <- mapview(d.x,zcol="Water System Ownership", alpha=0.8, layer.name = "All Water System Boundaries") +
  mapview(filter(aff,hhsize==4),stroke=TRUE,color="red",alpha.regions=0, layer.name = "Systems with price information", alpha = 0.5, col.regions="red")
#mapshot(m3,"Figures/Map3.html")
m3
```


SUmmarize ILI
```{r, audit}
audit <- read_csv("Data/audit_corrected.csv")
audit <- audit %>% 
  rename(PWSID=pwsid,
         ILI=PI_INFRASTRUCT_LEAKAGE_INDEX) %>%
  group_by(PWSID)  %>%
  distinct(PWSID,REPORTING_YEAR,.keep_all = TRUE) %>%
  summarise(ILI=mean(ILI,na.rm=TRUE))

```

Summarize SDWA status
```{r, include=FALSE}
 
v <- read_csv("Data/SDWA_SERIOUS_VIOLATORS.csv")
v <- v%>% dplyr::select(PWSID,FISCAL_YEAR,SERIOUS_VIOLATOR,STATE) %>% filter(STATE=="CA")
v$count=1
v <- v%>%group_by(PWSID)%>%summarize(years_serious_violater=sum(count))

```

Summarize shutoffs
```{r}
shutoffs <- ear %>% filter(substr(QuestionName,1,12)=="WR SHUT_OFFS" & Year==2018)

pws_shutoff_collect <- shutoffs %>% filter(QuestionName=="WR SHUT_OFFS Once No Collect" & is.na(QuestionResults))

shutoffs_total <- shutoffs %>%
  filter(QuestionName=="WR SHUT_OFFS Once SF Total" |
           QuestionName=="WR SHUT_OFFS More Than Once SF Total" |
           QuestionName=="WR SHUT_OFFS More Than Once MF Total" |
           QuestionName=="WR SHUT_OFFS Once SF Total") %>%
  group_by(PWSID, Year) %>%
  summarise(shutoffs=sum(as.numeric(QuestionResults),na.rm=TRUE))%>%
  select(PWSID,shutoffs) %>%
  distinct(.keep_all=TRUE) %>% semi_join(pws_shutoff_collect,by="PWSID")
```

Summarize subsidies
```{r}

subsidies <- ear %>% 
  filter(QuestionName=="WR LL Subsidies") %>% 
  filter(QuestionResults!="-") %>% 
  select(PWSID,QuestionResults,Year) %>% 
  rename(subsidy=QuestionResults) %>% distinct(.keep_all=TRUE) 

subs <- subsidies %>% 
  group_by(PWSID) %>%
  mutate(maxYear=max(Year)) %>%
  ungroup() %>%
  filter(Year == maxYear)
```

# Descriptive Statistics and Plots


Table 1:
```{r}
load("pwsdata.RData")
inc$UrbanRural <- "Urban"
inc$UrbanRural[which(is.na(inc$NAME))] <- "Rural"

inc$AreaType <- "Primary Residential/Municipal"
inc$AreaType[which(inc$SERVICE_AREA.SERVICE_AREA_TYPE_CODE=="MH")] <-"Mobile Home Parks"

inc$n <- 1
inc$small <- (inc$PWSID %in% small$PWSID)
inc <- filter(inc,!is.na(SERVICE_AREA.SERVICE_AREA_TYPE_CODE))
inc<- inc %>% mutate(UrbanAreaPop = case_when(
  Pop.y >= 1000000 ~ "> 1 million",
  Pop.y < 1000000 & Pop.y > 100000  & UrbanRural == "Urban" ~ "100k - 1 million",
   Pop.y < 100000 & Pop.y > 10000  & UrbanRural == "Urban" ~ "10k - 100k",
  Pop.y < 10000 & UrbanRural == "Urban" ~ "<10k Urban",
  UrbanRural == "Rural" ~ "Rural"
)
)

Tab1 <- inc %>% group_by(UrbanRural, AreaType) %>%
  summarise(count=sum(n),
            Population = sum(Pop.x)) %>%
  ungroup() %>%
  mutate(Percent = Population/sum(Population))

Tab2 <- inc %>% group_by(UrbanAreaPop,
                         `Water System Ownership`) %>%
  summarise(count=sum(n),
            Population = sum(Pop.x)) %>%
  ungroup() %>%
  mutate(Percent = 100*Population/sum(Population))
write.csv(Tab2,"tab2.csv")

##make table comparing Tab2 in non-small utilties
Tab3 <- inc %>% dplyr::filter(small == FALSE) %>% group_by(UrbanAreaPop,
                         `Water System Ownership`) %>%
  summarise(count=sum(n),
            Population = sum(Pop.x)) %>%
  ungroup() %>%
  mutate(Percent = 100*Population/sum(Population))
write.csv(Tab3,"tab3.csv")

hist <- inc %>% dplyr::filter(small == TRUE)

inc2 <- inc %>% dplyr::filter(small == FALSE)
### Figure 3
inc2$ownership <- inc2$`Water System Ownership`
inc2 <- inc2 %>% mutate(UrbanAreaPop = case_when(
  UrbanAreaPop=="<10k Urban" ~ "4. < 10k Urban",
  UrbanAreaPop=="Rural" ~ "5. Rural",
  UrbanAreaPop=="> 1 million" ~ "1. > 1 mill.",
  UrbanAreaPop=="100k - 1 million" ~ "2. 100k-1 mill.",
  UrbanAreaPop=="10k - 100k" ~ "3. 10k - 100k"
))

ggplot2.violinplot(data=inc2, xName='UrbanAreaPop',yName='income20',
    groupName='ownership', legendPosition="right")
#    faceting=TRUE, facetingVarNames=c("UrbanAreaPop"))

f3.1<-ggplot2.boxplot(data=inc2,yName='income50', faceting=TRUE, facetingVarNames=c("UrbanAreaPop"),groupName='ownership',legendPosition="none", xtitle="Ownership", ytitle = "Median HH Income",brewerPalette = "Dark2")

f3.2<-ggplot2.boxplot(data=inc2,yName='income20', faceting=TRUE, facetingVarNames=c("UrbanAreaPop"),groupName='ownership',legendPosition="none", xtitle="Ownership", ytitle = "20th Percentile HH Income",brewerPalette = "Dark2")

f3.3<-ggplot2.boxplot(data=inc2,yName='perc_below_200FPL', faceting=TRUE, facetingVarNames=c("UrbanAreaPop"),groupName='ownership',legendPosition="none", xtitle="Ownership", ytitle = "% Pop <200% FPL",brewerPalette = "Dark2")

f3.4<-ggplot2.boxplot(data=inc2,yName='gini', faceting=TRUE, facetingVarNames=c("UrbanAreaPop"),groupName='ownership',legendPosition="none", xtitle="Ownership", ytitle = "Gini Coefficient",brewerPalette = "Dark2")

### Regressions
m1 <- felm(data=inc2,income20 ~ `Water System Ownership` |0|0|County)
m2 <- felm(data=inc2,income50 ~ `Water System Ownership` |0|0|County)
m3 <- felm(data=inc2,perc_below_200FPL ~ `Water System Ownership` |0|0|County)
m4 <- felm(data=inc2,gini ~ `Water System Ownership` |0|0|County)
m1.f <- felm(data=inc2,income20 ~ `Water System Ownership` |County|0|County)
m2.f <- felm(data=inc2,income50 ~ `Water System Ownership` |County|0|County)
m3.f <- felm(data=inc2,perc_below_200FPL ~ `Water System Ownership` |County|0|County)
m4.f <- felm(data=inc2,gini ~ `Water System Ownership` |County|0|County)

stargazer::stargazer(m2,m2.f,m1,m1.f,m3,m3.f,m4,m4.f,type="html",align=TRUE,digits=2,out="regs.html")

```
make big table
```{r}
D <- aff 

D <- left_join(D,audit,by="PWSID") # add ILI

D <- left_join(D,v,by="PWSID") #add SDWA violator status
  D$years_serious_violater[which(is.na(D$years_serious_violater))] <- 0

D <- left_join(D, shutoffs_total, by="PWSID") #add shutoffs_total  
D$shutoffs_perc = D$shutoffs/as.numeric(D$ServConn)

D <- left_join(D,subs,by="PWSID") ## add subsidy programs

save(D,file="Data/FinalData.rds")
```

 
## Bill compare
```{r}
pl_pws2 <- st_drop_geometry(pl_pws)
esquisser(pl_pws2)

View(ear)
table(ear$QuestionName)
x <- distinct(ear$QuestionName)
q <- dplyr::distinct(ear$QuestionName)
q <- dplyr::distinct(ear,QuestionName)
View(q)
hcf <- filter(ear,QuestionName== "WR 6 HCF DW Charges")
hcf <- dplyr::filter(ear,QuestionName== "WR 6 HCF DW Charges")
View(hcf)
table(hcf$Year)
hcf <- dplyr::filter(ear,QuestionName== "WR 6 HCF DW Charges" & Year==2017)
hcf
hcf.d <- dplyr::distinct(hcf,PWSID)
bills3 <- bills <- dplyr::filter(bills,hhsize==3)
bill_compare <- left_join(hcf.d,bills3,by="PWSID")
bill_compare <- dplyr::left_join(hcf.d,bills3,by="PWSID")
bill_compare <- dplyr::left_join(hcf.d,bills3,by=c("PWSID"="pwsid"))
hcf.d <- dplyr::distinct(hcf,PWSID,.keep_all=TRUE)
bill_compare <- dplyr::left_join(hcf.d,bills3,by=c("PWSID"="pwsid"))
View(bill_compare)
bill_compare$ear_bill <- as.numeric(gsub("$","",bill_compare$QuestionResults))
plot(bill_compare$ear_bill ~ bill_compare$bill)

```

descriptive stats
```{r}
rm(list=ls())
load("Data/FinalData.rds")
D.f <- D
D <- D.f


incs <- inc2 %>% select(PWSID,gini,perc_below_200FPL,income20,income50,ownership,Pop.y,UrbanRural,UrbanAreaPop)

D <- left_join(D,incs,by="PWSID")

D$AR20 <- 12*D$bill/D$income20
D$AR50 <- 12*D$bill/D$income50
D$hhsize_cat <- as.character(D$hhsize)

counties <- sf::read_sf("https://info.geoconnex.us/collections/counties/items?STATEFP=06&limit=500")

D2 <- st_intersection(D,st_transform(counties,3310))
m.ar20 <- felm(formula = AR20 ~ ownership + log(Pop) + log(Pop.y) | 0 |      0 | COUNTYFP, data = filter(D2, hhsize == 4)) 
m.ar50 <- felm(formula = AR50 ~ ownership + log(Pop) + log(Pop.y) | 0 |      0 | COUNTYFP, data = filter(D2, hhsize == 4)) 

m.shutoff <- felm(formula = shutoffs_perc ~ ownership + log(Pop) + AR20 + perc_below_200FPL| 0 |      0 | COUNTYFP, data = filter(D2, hhsize == 4)) 

stargazer::stargazer(m.ar20,m.ar50,m.shutoff,type="html",align=TRUE,digits=2,out="regs2.html")

f6<-ggplot2.boxplot(data=filter(D,hhsize==4),yName='AR20', faceting=TRUE, facetingVarNames=c("UrbanAreaPop","log10PopCat"),groupName='ownership',legendPosition="none", xtitle="Ownership", ytitle = "AR20",brewerPalette = "Dark2",facetingScales="free")

D <- D %>% ungroup() %>% distinct(PWSID,hhsize,.keep_all = TRUE)

D1 <- D%>%filter(hhsize==1) 
D2 <- D%>%filter(hhsize==2) %>% select(PWSID,consumption,bill,AR20) %>% rename(consumption_2=consumption,
                                                                                      bill_hhsize2=bill, AR20_hhsize2 = AR20) %>% st_drop_geometry()
D3 <- D%>%filter(hhsize==3) %>% select(PWSID,consumption,bill,AR20) %>% rename(consumption_3=consumption,
                                                                                      bill_hhsize3=bill, AR20_hhsize3 = AR20)  %>% st_drop_geometry()
D4 <- D%>%filter(hhsize==4) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_4=consumption,
                                                                                      bill_hhsize4=bill, AR20_hhsize4 = AR20)  %>% st_drop_geometry()
D5 <- D%>%filter(hhsize==5) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_5=consumption,
                                                                                      bill_hhsize5=bill, AR20_hhsize5 = AR20) %>% st_drop_geometry()
D6 <- D%>%filter(hhsize==6) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_6=consumption,
                                                                                      bill_hhsize6=bill, AR20_hhsize6 = AR20) %>% st_drop_geometry()
D7 <- D%>%filter(hhsize==7) %>% select(PWSID,consumption,bill,AR20)%>% rename(consumption_7=consumption,
                                                                                      bill_hhsize7=bill, AR20_hhsize7 = AR20) %>% st_drop_geometry()



D.wide <- D1 %>% 
  left_join(D2,by="PWSID") %>%
  left_join(D3,by="PWSID") %>%
  left_join(D4,by="PWSID") %>%
  left_join(D5,by="PWSID") %>%
  left_join(D6,by="PWSID") %>%
  left_join(D7,by="PWSID") 

D.wide$geometry <- NULL
library(psych)

D.wide <- filter(D.wide,!is.na(AR20))
D.wide2 <- D.wide %>% select(PWSID,Pop,`Water System Ownership`, 
                  `20th Percentile`, `50th Percentile`,
                 ILI, years_serious_violater, shutoffs_perc,subsidy,
                 bill_type,bill,bill_hhsize2,bill_hhsize3,bill_hhsize4,bill_hhsize5,bill_hhsize6,bill_hhsize7,
                 AR20,AR20_hhsize2,AR20_hhsize3,AR20_hhsize4,AR20_hhsize5,AR20_hhsize6,AR20_hhsize7)

D.wide2$bill_type[which(D.wide2$bill_type %in% c("1.49*usage_ccf","3.04*usage_ccf*1.333"))] <- "Uniform"

st(D.wide2, group='Water System Ownership', group.test=TRUE, digits=2)

D.wide3 <- filter(D.wide2,`Water System Ownership` %in% c("Local Government","Privately owned, PUC-regulated, for profit water company"))

st(D.wide3, group='Water System Ownership', group.test=TRUE, digits=2)
D.wide3$subsidy[which(is.na(D.wide3$subsidy))] <- "NA"

f4<-ggplot(filter(D.wide2,Pop>0), aes(x=Pop,y=AR20_hhsize4,color=`Water System Ownership`, shape=subsidy, cex=2))  + geom_hline(yintercept=3.5, color="green", lwd=2)+ geom_point(size=2) + scale_x_log10() + theme_dark() + scale_color_viridis_d() + theme(legend.position=c(0.7,0.6)) + xlab("Service Population (log10 scale)") + ylab("AR20 for 4-person Household")  # + geom_smooth(formula=y~log10(x),method='lm')
png("Figures/Figure4.png")
f4
dev.off()

f4

f5 <- ggplot(D.wide3, aes(x=AR20_hhsize4, color=`Water System Ownership`), size=4) +
  geom_density(lwd=2) + 
  scale_color_viridis_d() + 
  theme_dark() + 
  xlab("AR20")


f6 <- ggplot(D.wide3, aes(x=shutoffs_perc*100, color=`Water System Ownership`), size=4) +
  geom_density(lwd=2) + 
  scale_color_viridis_d() + 
  theme_dark() + 
  xlab("Shutoff rate")

f7 <- ggplot(D.wide3, aes(x=ILI, color=`Water System Ownership`), size=4) +
  geom_density(lwd=2) + 
  scale_color_viridis_d() + 
  theme_dark() + 
  xlab("ILI")

f8 <- ggplot(D.wide3, aes(x=`years_serious_violater`, color=`Water System Ownership`), size=4) +
  geom_density(lwd=2) + 
  scale_color_viridis_d() + 
  theme_dark() + 
  xlab("Years in which USEPA has labelled serious SDWA Violator")

F5 <- ggarrange(f5,f6,f7,f8, labels = c("A: AR20 (HH size 4)", "B: Shutoff Rate (%)","C: ILI", "D: SDWA Violation"),
                common.legend=TRUE, legend="bottom")

F5

inv <- read_excel("Data/EAR/inventory.xlsx",
                  sheet = "SDWISWaterSystemInventory071620") 

inv <- select(inv,PWSID,County)

D.wide2 <- left_join(D.wide2,inv,by="PWSID") 
D.wide3 <- left_join(D.wide3,inv,by="PWSID") 
D.wide3 <- filter(D.wide3,Pop>0)
D.wide3$shutoffs_perc <- 100*D.wide3$shutoffs_perc

myfelmAR <- function(data){

list.B <- list()
list.B$B2.2 <- felm(data=data,AR20_hhsize2 ~ `Water System Ownership` + log(Pop)  + `50th Percentile`|0|0|County)
list.B$B3.2 <- felm(data=data,AR20_hhsize3 ~ `Water System Ownership` + log(Pop) + `50th Percentile` |0|0|County)
list.B$B4.2 <- felm(data=data,AR20_hhsize4 ~ `Water System Ownership` + log(Pop) + `50th Percentile` |0|0|County)
list.B$B5.2 <- felm(data=data,AR20_hhsize5 ~ `Water System Ownership` + log(Pop) + `50th Percentile` |0|0|County)
list.B$B6.2 <- felm(data=data,AR20_hhsize6 ~ `Water System Ownership` + log(Pop) + `50th Percentile` |0|0|County)
list.B$S2.2 <- felm(data=filter(data,subsidy!="NA"),shutoffs_perc ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + AR20_hhsize4 + subsidy|0|0|County)
return(list.B)
}  

myfelmILI <- function(data){

list.B <- list()
list.B$B2.1 <- felm(data=data,ILI ~ log(Pop) + `50th Percentile` +  bill_hhsize4|0|0|County)
list.B$B2.2 <- felm(data=data,ILI ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + bill_hhsize4|0|0|County)
list.B$B2.3 <- felm(data=data,ILI ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + bill_hhsize4|County|0|County)


return(list.B)
}  

myfelmV <- function(data){

list.B <- list()
list.B$B2.1 <- felm(data=data,`years_serious_violater` ~ log(Pop) + `50th Percentile` +  bill_hhsize4|0|0|County)
list.B$B2.2 <- felm(data=data,`years_serious_violater` ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + bill_hhsize4|0|0|County)
list.B$B2.3 <- felm(data=data,`years_serious_violater` ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + bill_hhsize4|County|0|County)


return(list.B)
}  

myfelmSO <- function(data){

list.B <- list()
list.B$B2.1 <- felm(data=filter(data,subsidy!="NA"),shutoffs_perc ~ log(Pop) + `50th Percentile` + AR20_hhsize4 + subsidy |0|0|County)
list.B$B2.2 <- felm(data=filter(data,subsidy!="NA"),shutoffs_perc ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + AR20_hhsize4 + subsidy|0|0|County)
list.B$B2.3 <- felm(data=filter(data,subsidy!="NA"),shutoffs_perc ~ `Water System Ownership` + log(Pop)  + `50th Percentile`  + AR20_hhsize4 + subsidy|County|0|County)


return(list.B)
}  


myfelmP <- function(data){
  
list.B <- list()
  list.B$I2.2 <- felm(data=data,ILI ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + bill_hhsize4|0|0|County)
  list.B$V2.2 <- felm(data=data,`years_serious_violater` ~ `Water System Ownership` + log(Pop)  + `50th Percentile` + bill_hhsize4|0|0|County)
  return(list.B)
}

  
```
# Regressions
```{r, results="asis"}
l1 <- myfelmAR(D.wide3)
l2 <- myfelmSO(D.wide3)
l3 <- myfelmILI(D.wide3)
l4 <- myfelmV(D.wide3)

l5 <- myfelmAR(D.wide3)
lP <-myfelmP(D.wide3)

stargazer(l1,type="html",out="Tables/AR20Regression.html")

stargazer(l2,type="html",out="Tables/SORegression.html")
stargazer(l3,type="html",out="Tables/ILIRegression.html")
stargazer(l4,type="html",out="Tables/VRegression.html")

stargazer(l5,type="html",out="Tables/ERegression.html")
stargazer(lP,type="html",out="Tables/PRegression.html")

stargazer(l1)
stargazer(l2)
stargazer(l3)
stargazer(l4)
stargazer(l5)
```